%-------------------------------------------------------------------------------
%   SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%   CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
    \cventry
    {Solutions Architect [Python/Devops/Testing]} % Job title
    {Ericsson India} % Organization
    {Kolkata, West Bengal, INDIA} % Location
    {Sep, 2018 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Working on different projects on NFVI, Openstack, Kubernetes}
        \item {Implemented Sonobuoy Testing Framework with additional capablities using python unittests .}
        \item {Working as a lead Contributer for a major American telco operator's cloud platform }
        \item {Worked on several POC projects in Docker, Kubernetes, ansible, focusing on high-availability, fault tolerance, and auto-scaling. }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer III [Python/Devops]} % Job title
    {Terdata Labs} % Organization
    {Hyderabad, Telangana, INDIA} % Location
    {Apr, 2018 - Sep, 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented python based web app to cater different needs .}
        \item {Implemented ELK Automation on ansible to add n host for monitoring. }
        \item {Worked on writing Vagrant files for different application }
        \item {Worked on several POC projects in Docker, Kubernetes, ansible, focusing on high-availability, fault tolerance, and auto-scaling. }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer [Python]} % Job title
    {Pramati Technologies} % Organization
    {Hyderabad, Telangana, INDIA} % Location
    {Apr, 2015 - Mar, 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented djangorestframework RESTful API server for internal projects.}
        \item {Implemented Data driven Framework in python/djangorestframework frontend/backend. }
        \item {Worked on Automation Framework in Ansible to deploy Openstack for one of the largest Telecom Provider. }
        \item {Worked on several POC projects in Docker, Kubernetes, ansible, focusing on high-availability, fault tolerance, and auto-scaling. }
        \item {Developed an easy-to-use Payment module which connects to major PG(Payment Gateway).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer [Python]} % Job title
    {MindFire Solutions} % Organization
    {Bhubaneswar, Orrisa, INDIA} % Location
    {Nov. 2012 - Apr. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on several Odoo (formerly openerp) projects.}
        \item {Worked on Customized ERP Application for Custom Brokerage and warehousing using odoo framework in python.}
        \item {Worked on Web based ERP Solutions for Importers and Exporters using PHP, EXTjs, Mysql.}
      \end{cvitems}
      % \begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      % \end{cvsubentries}
    }

%---------------------------------------------------------
  \cventry
    {Web Engineer  [PHP]} % Job title
    {Acumen Consultancy PvtLtd} % Organization
    {Kolkata, WestBengal,  INDIA} % Location
    {Jun, 2010 - Nov. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on IMS-Pharmastat, web based CMS using PHP (Codeigniter), Javascript, Mysql. (http://imspharmastat.fr/)}
        \item {Worked on UBI-France, Web Based Doctor Directory Listing using PHP (Codeigniter), Javascript, Mysql.}
        \item {Worked on Open2leads, Question and Answer Forum for B2B with social-networking features, Using  PHP (symfony), JavaScript, MySQL.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
